A DPG method for compressible flow problems

### 2012-06-20 docs/Jesse/Proposal/NSNotes.tex
modifications to thesis (adding of inviscid/incompressible stuff, mod of area requirement, mod of NS notes

For $p=2$, after six refinements, the mesh contained 1410 elements and 187605 global dofs, with a total DPG energy error of $.000753$. Comparatively, for $p=3$, the mesh contained only 444 elements and 97403 global dofs, with a total DPG eneryg error of $0.000676$ after five refinements.

\begin{figure}[!h]
\centering
\subfigure[$p=2$]{\includegraphics[scale=.5]{figs/Re1000p2/mesh.pdf}}
\subfigure[$p=3$]{\includegraphics[scale=.5]{figs/Re1000p3/mesh.pdf}}
\caption{Adaptive mesh after six refinements for $p=2$ and five refinements for $p=3$ with $\Reyn = 1000$.}
\label{fig:MeshRe500}
\end{figure}

>>>>

For $p=2$, after six refinements, the mesh contained 1134 elements and 150489 global dofs, with a total DPG energy error of $.000753$.

\begin{figure}[!h]
\centering
\subfigure[$p=2$]{\includegraphics[scale=.5]{figs/Re1000p2/mesh.pdf}}
%\subfigure[$p=3$]{\includegraphics[scale=.5]{figs/Re1000p3/mesh.pdf}}
\caption{Adaptive mesh after six refinements for $p=2$
% and five refinements for $p=3$ 
with $\Reyn = 1000$.}
\label{fig:MeshRe500}
\end{figure}

### 2012-06-20 docs/Jesse/Proposal/areaReq.tex
modifications to thesis (adding of inviscid/incompressible stuff, mod of area requirement, mod of NS notes

\begin{itemize}
\item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}} 
\item{\textbf{Proposed: Higher Reynolds number, ramp problem, Gaussian bump, airfoil.}}
\item{\textbf{Proposed: regularized Euler.}}
\end{itemize}

>>>>

\begin{itemize}
\item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}}

I have applied the DPG method to a several convection diffusion problems which mimic difficult problems in compressible flow simulations, including boundary layer and closed streamline problems.  I have also solved the viscous Burgers' equation as an extension of DPG to nonlinear problems. I have also explored the regularization of the pure convection equation using the full convection-diffusion equation in the small-viscosity limit. DPG has also been applied to the Navier-Stokes equations to achieve a solution to the flat plate problem for $\Reyn = 1000$.

\item{\textbf{Proposed: Higher Reynolds number, ramp problem, Gaussian bump, airfoil.}}

The effectiveness of DPG as a numerical method for compressible flow will be assessed with the application of DPG to common transonic and superonic benchmark problems.  In particular, I will use DPG to solve the flat plate problem, the ramp problem, flow over a Gaussian bump, and flow over an airfoil over a range of Mach numbers and laminar Reynolds numbers.

\item{\textbf{Proposed: regularized Euler.}}

Time permitting, I will also explore the regularization of the Euler equations using the full Navier-Stokes equations in the inviscid limit.

### 2012-06-20 docs/Jesse/Proposal/problemRange.tex
modifications to thesis (adding of inviscid/incompressible stuff, mod of area requirement, mod of NS notes

\todo{reference Stokes, cite Nate}
\cite{stokesDPG}

@@

@@

The Burgers' equation is physically derived from the incompressible Navier-Stokes equations under the assumption that $\grad p \approx 0$, or that the pressure field is near constant. A feature of the Burgers' equation not present in convection-diffusion is that, due to the presence of the nonlinear term, it can develop shock discontinuities in its solutions in finite time.  The Burgers' equation has also been used to study the phenomenon of turbulence; however, the Burgers equation does not exhibit the chaotic nature and sensitivity to initial conditions that characterizes turbulence as observed in the full and incompressible Navier-Stokes equations. In the scope of this dissertation proposal, Burgers shall be used as to test the extension of our numerical method to nonlinear problems.

>>>>

Under appropriate assumptions on the behavior of density and temperature, the behavior of the compressible Navier-Stokes equations can be sufficiently represented by the incompressible Navier-Stokes equations for low speed laminar fluid flows.

For viscous ``creeping'' flows, the incompressible Navier-Stokes equations reduce down to the Stokes equations. \cite{stokesDPG}

@@

The scalar convection-diffusion equation is also mathematically important

@@

The Burgers' equation is physically derived from the incompressible Navier-Stokes equations under the assumption that $\grad p \approx 0$, or that the pressure field is near constant. A feature of the Burgers' equation not present in convection-diffusion is that, due to the presence of the nonlinear term, it can develop shock discontinuities in its solutions in finite time.  The Burgers' equation has also been used to study the phenomenon of turbulence; however, the Burgers equation does not exhibit the chaotic nature and sensitivity to initial conditions that characterizes turbulence as observed in the full and incompressible Navier-Stokes equations.

The Burgers' equation is also the simplest nonlinear extension of the linear convection-diffusion equation, and exact solutions can sometimes be found using the method of characteristics. In the scope of this dissertation proposal, Burgers shall be used as to test the extension of our numerical method to nonlinear problems.
